Inefficient Concessions and Mediation

### 2021-01-20 notes.tex
fix mistake in W0 and W1 calculations (there's more to do but I don't think I need it for this revision)

When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$

@@

When $e=1$, welfare is $\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$ \\

@@

\vskip.2in
Parameterization 5: $W1 > W0 > We$ (mediator). Mediator optimally chooses $e=0.03$
\begin{itemize}
	\item $T = 6, \ W = 8, \ D = 5, \ p = .5, \ \de_l = .2, \ \de_h = .9$
\end{itemize}

\vskip.2in
Parameterization 6: $We > W1 > W0$, $54 > 7.33 > 7$. Mediator optimally chooses $e=0.24$. Optimal gift is 50, effective gift is 12, vs. $g1 = .667$ and $g0 = 1$
\begin{itemize}
	\item $T = 1, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 15/16=0.9375$
\end{itemize}

@@

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item Can I do new mediator theorem in the same form as the one that's currently in the paper?
					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
						\begin{itemize}
							\item Two differences: Mediator gets you some value of the gift $pTeg_M$; gift under mediator typically has to be larger--it takes more to disincentivize low type from lying because the payoff is better
						\end{itemize}
					\item If you can sustain $e=1$ with no mediator, mediator can still be better
						\begin{itemize}
							\item Again, if mediator is good, it's REALLY good.
							\item The benefit of $eg_M$ is muted versus $g^1$, but there is no harm from $g_M$ while there is harm from $g^1$. Cost of gift will always be larger under mediator because it goes to infinity at the optimal $e$
						\end{itemize}
					\item Sufficient condition for where welfare goes to positive $\infty$ to the left of the $e$ asymptote
						\begin{itemize}
							\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard. But I have developed an intuitive sufficient condition. See end of Section~\ref{sec:WM1}
						\end{itemize}
					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable is strictly smaller than $\de^h$. \textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
							\begin{itemize}
								\item This is nice, but I'm not sure it helps with the narrative of the story.
									\begin{itemize}
										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
											\begin{itemize}
												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
												\item Should I compare grim trigger welfare to see which is higher?
											\end{itemize}
									\end{itemize}
							\end{itemize}
			\end{itemize}

>>>>

When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
\textbf{THE ABOVE EQUATION IS wrong. We should subtract off $(1-p)g^0$ since $p$ of the time you receive a gift} \\

@@

When $e=1$, welfare is $\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$ \\
\textbf{THE ABOVE EQUATION IS wrong. We should subtract off $(1-p)g^1$ since $p$ of the time you receive a gift} \\

@@

\vskip.2in
Parameterization 5: $We > W1 > W0$. Asymptote at $e = 03759...$ (Was incorrect before I understood the asymptote: $W1 > W0 > We$ (mediator). Mediator optimally chooses $e=0.03$(
\begin{itemize}
	\item $T = 6, \ W = 8, \ D = 5, \ p = .5, \ \de_l = .2, \ \de_h = .9$
\end{itemize}

\vskip.2in
Parameterization 6: $We > W1 > W0$, $54 > 7.33 > 7$. Mediator optimally chooses $e=0.24$ (0.25 is the asymptote). Optimal gift is 50, effective gift is 12, vs. $g1 = .667$ and $g0 = 1$
\begin{itemize}
	\item $T = 1, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 15/16=0.9375$
\end{itemize}

\vskip.2in
Parameterization 7: $We > W0 > W1$, $42.33 > 4.96 > 2.83$. Mediator optimally chooses $e=0.28$ (0.28571 is the asymptote). Optimal gift is 75, effective gift is 21, vs. $g1 = .428$ and $g0 = .75$
\begin{itemize}
	\item $T = 0.5, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 61/64=0.953125$
\end{itemize}

@@

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
					\item Can I do new mediator theorem in the same form as the one that's currently in the paper?
					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
						\begin{itemize}
							\item Two differences: Mediator gets you some value of the gift $pTeg_M$; gift under mediator typically has to be larger--it takes more to disincentivize low type from lying because the payoff is better
						\end{itemize}
					\item If you can sustain $e=1$ with no mediator, mediator can still be better
						\begin{itemize}
							\item Again, if mediator is good, it's REALLY good.
							\item The benefit of $eg_M$ is muted versus $g^1$, but there is no harm from $g_M$ while there is harm from $g^1$. Cost of gift will always be larger under mediator because it goes to infinity at the optimal $e$
						\end{itemize}
					\item Sufficient condition for where welfare goes to positive $\infty$ to the left of the $e$ asymptote
						\begin{itemize}
							\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard. But I have developed an intuitive sufficient condition. See end of Section~\ref{sec:WM1}
						\end{itemize}
			\end{itemize}
